---
title: "Bibliometric analysis of peat review - Agriculture corpus"
author: "Matt"
date: "3 6 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# load libraries
library(PRISMAstatement)
library(tidyverse)
library(bibliometrix)
library(litsearchr)
library(revtools)

```

## Agriculture Group

Web of Science search:

((((peat  OR peatland  OR peatlands  OR bog  OR fen  OR mire)  NOT  ((tropic* NEAR/3 peat*)  OR  (tropic* NEAR/3 fen*)  OR  subtropic*  OR  malays*  OR  indones*  OR  india*  OR  amason*  OR  amazon*  OR  brazil*  OR  congo*)))  AND ((peat* NEAR/5 (agricultur* OR cultivated OR arable)) OR (drain* NEAR/5 agricultur*)))

## Prisma statement

```{r prisma, echo=FALSE}
prisma(found = 617,
       found_other = 0,
       no_dupes = 0, 
       screened = 0, 
       screen_exclusions = 0, 
       full_text = 0,
       full_text_exclusions = 0, 
       qualitative = 0, 
       quantitative = 0,
       width = 200, height = 200)
```

## {Bibliometrix} 

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
filelist=list.files(paste0(here::here(),"/data"), pattern="^.*Agriculture.*.bib") 

M <- convert2df(file = c(paste0(here::here(),"/data/",filelist[1]), paste0(here::here(),"/data/",filelist[2])), dbsource = "wos", format = "bibtex")

```

```{r look at biblio summary, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
results <- biblioAnalysis(M, sep = ";")
S <- summary(object = results, k = 40, pause = FALSE)
keywordDF=cbind(S$MostRelKeywords[1], S$MostRelKeywords[2])
keywordPluss=cbind(S$MostRelKeywords[3], S$MostRelKeywords[4])
```

```{r keywrod plot, echo=FALSE, message=FALSE, warning=FALSE, }
keywordDF %>%
  janitor::clean_names() %>%
  mutate(author_keywords_de=tolower(author_keywords_de)) %>%
  mutate(articles=as.numeric(articles)) %>% 
  top_n(.,40) %>% 
  ggplot(aes(reorder(author_keywords_de,articles),articles))+
    geom_histogram(stat="identity", fill=NinaR::nina_colors[1])+
  coord_flip()+
  labs(x="Top 40 Keywords", y="Frequency (n papers)")+
  ggtitle("Frequency of author keywords")+
  theme_minimal()
```

## Keywords plus (words in titles of cited references)

```{r keywordplus plot, echo=FALSE, message=FALSE, warning=FALSE }
keywordPluss %>%
  janitor::clean_names() %>%
  mutate(keywords_plus_id=tolower(keywords_plus_id)) %>%
  mutate(articles=as.numeric(articles)) %>% 
  top_n(.,40) %>% 
  ggplot(aes(reorder(keywords_plus_id,articles),articles))+
    geom_histogram(stat="identity", fill=NinaR::nina_colors[1])+
  coord_flip()+
  labs(x="Top 40 Keywords plus", y="Frequency (n papers)")+
  ggtitle("Frequency of author keywords")+
  theme_minimal()
```


## Keyword co-occurrence network - shared keywords between publications

```{r keyword network,, echo=FALSE, message=FALSE, warning=FALSE }

# Create keyword co-occurrences network
NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")

# full network
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 617, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,label= FALSE)
```

## Most common keyword combinations

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(igraph)
mylist=list(
E(net$graph)[373],
E(net$graph)[551],
E(net$graph)[8],
E(net$graph)[870]
#,
#E(net$graph)[389],
#E(net$graph)[2069],
#E(net$graph)[186]
)
mylist

```

## Trends in cluster membership 

```{r trends in memembership, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#get the cluster for each paper
# net$cluster_res
# net$community_obj$memberships
mat=as.data.frame(t(net$community_obj$memberships))

membership=data.frame("Authors"=M$AU, "Title"=M$TI, "Year"=M$PY, "cluster"=mat$V2)
#clusternames
net$cluster_res %>% 
  group_by(cluster) %>%
  mutate(ismax=if_else(btw_centrality==max(btw_centrality), "Yes","No")) %>% 
  filter(ismax=="Yes") %>% 
  select(vertex)->cluster_names
  

cluster_names=cluster_names[c(1:7,18:21 ),]


```


```{r plot trend,echo=FALSE, message=FALSE, warning=FALSE}
membership=membership %>% 
  inner_join(cluster_names)

pal=RColorBrewer::brewer.pal(dim(cluster_names)[1],name ="Paired" )
  
membership %>% 
  group_by(vertex) %>% 
  ggplot(aes(Year)) +
  geom_histogram(fill="darkred")+
  theme_classic()+
  facet_wrap(~vertex)
```

## Thematic evolution of the corpus

```{r Thematic evolution of the corpus, echo=FALSE, message=FALSE, warning =FALSE}

years=c(1995,2000, 2010, 2015)

nexus <- thematicEvolution(M,field="ID",years=years,n=100,minFreq=2)
plotThematicEvolution(nexus$Nodes,nexus$Edges)

```


## LDA Topic models


```{r topic models,echo=FALSE, message=FALSE, warning=FALSE}
topics <- readRDS("C:/Users/matthew.grainger/Documents/Projects_in_development/PeatReview/Reports/data/topics.rds")
#result <-ldatuning::FindTopicsNumber(
#  topics$dtm,
#  topics = seq(from = 25, to = 40, by = 1),
#  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
#  method = "Gibbs",
#  control = list(seed = 77),
#  mc.cores = 2L,
#  verbose = TRUE
#)
#saveRDS(result, "data/result.rds")
result <- readRDS("C:/Users/matthew.grainger/Documents/Projects_in_development/PeatReview/Reports/data/result.rds")
ldatuning::FindTopicsNumber_plot(result)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
tms=topicmodels::LDA(topics$dtm,k=38)
tmResult <- topicmodels::posterior(tms)
beta <- tmResult$terms   # get beta from results
theta <- tmResult$topics 
```


## Primary topics

```{r topicnames, echo=FALSE, message=FALSE, warning=FALSE}
topicNames <- apply(lda::top.topic.words(beta, 5, by.score = T), 2, paste, collapse = " ")
countsOfPrimaryTopics <- rep(0, 38)
names(countsOfPrimaryTopics) <- topicNames
for (i in 1:617) {
  topicsPerDoc <- theta[i, ] # select topic distribution for document i
  # get first element position from ordered list
  primaryTopic <- order(topicsPerDoc, decreasing = TRUE)[1] 
  countsOfPrimaryTopics[primaryTopic] <- countsOfPrimaryTopics[primaryTopic] + 1
}

cntsPrim=data.frame(keyName=names(countsOfPrimaryTopics), value=countsOfPrimaryTopics, row.names=NULL)

cntsPrim %>% 
  ggplot(aes(reorder(keyName,value), value)) + 
  geom_histogram(stat="identity", fill=NinaR::nina_colors[1])+
  coord_flip()+
  labs(x="Topics", y="Frequency")+
  ggtitle("Frequency of primary topics")+
  theme_minimal()
  
```

